\documentclass[a4paper,10pt,twoside]{article}
% \pdfoutput=1 

\usepackage[bookmarks=true,colorlinks=true]{hyperref}

\usepackage{bookmark}
\bookmarksetup{
 numbered, 
 open,
}


\usepackage{todonotes}

\usepackage{amssymb,amsmath}       % Equations
\usepackage{array}
\usepackage{bm}                    % Bold math symbols
\usepackage{epsfig}
\usepackage{float}
\usepackage{graphicx,color,psfrag} % Graphics, Figures
\usepackage[export]{adjustbox}
% \usepackage{subcaption}
\usepackage{tikz}

\usepackage{multirow}              % For Tables
\usepackage{tabularx}              % Tables
\usepackage{wrapfig}
\usepackage[algoruled]{algorithm2e}
\SetStartEndCondition{ }{}{}%
\SetKwProg{Fn}{def}{\string:}{}
\SetKwFunction{Range}{range}%%
\SetKw{KwTo}{in}\SetKwFor{For}{for}{\string:}{}%
\SetKwIF{If}{ElseIf}{Else}{if}{:}{elif}{else:}{}%
\SetKwFor{While}{while}{:}{}%
% \renewcommand{\forcond}{$i$ \KwTo\Range{$n$}}
\AlgoDontDisplayBlockMarkers\SetAlgoNoEnd\SetAlgoNoLine%


%% enumitem 
% \labelindent is defined in both IEEEtrans and
% enumitem. \let\labelindent\relax kind-of disables \labelindent
% defined in IEEEtrans, hence avoiding the name clash.
\let\labelindent\relax
\usepackage[inline]{enumitem}

% variables
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
% acronyms
\newcommand{\ie}{{\textit{i.e.}}}
\newcommand{\etal}{\textit{et~al.}}

% theorem environment
\usepackage{amsthm}
\newtheoremstyle{exercise} % name
    {\topsep}                    % Space above
    {\topsep}                    % Space below
    {}                   		 % Body font
    {}                           % Indent amount
    {\bfseries}                   % Theorem head font
    {.}                          % Punctuation after theorem head
    {.5em}                       % Space after theorem head
    {}  % Theorem head spec (can be left empty, meaning ‘normal’)

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
% \newtheorem{exercise}{Exercise}[section]
\newtheorem{example}[theorem]{Example}

% Redefine exercise formating 
% \theoremstyle{plain}
\theoremstyle{exercise}
\newtheorem{exercise}{Exercise}


% figures path
\graphicspath{{figures/}}

% \overrideIEEEmargins
% set margins
\setlength{\floatsep}{2pt plus 1pt minus 1pt}
\setlength{\textfloatsep}{5pt plus 1pt minus 2pt}

%% TITLE
\title{Homework 3}
%% AUTHOR
\author{Pham Tien Hung, Zhang Xu}

%% DATE
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\maketitle
\begin{exercise}[Sort $k$ sorted lists.]\

Idea is to use a Priority Queue (min heap) to keep the smallest
elements $k$ lists. Then at each iteration, we remove the smallest
element from the Queue, pop that element from its list and add in
the next smallest element in that list into the queue.
\begin{algorithm}[h]
	\caption{Sort $k$ sorted lists ($L[1...k][:]$)}
	$Queue$ = Make-queue()\;
	Let $X$ be an empty list\;
	\For{$i$ in $[1,...,k]$}{
		Add($i$, $L[i][1]$)\;
	}
	\For{$i$ in $[1,...,n]$}{
		$j$ = Extract-min($Queue$) \tcp*{pop the $j$-th list}
		$x$ = pop($L[j][1]$) \tcp*{Remove the first element}
		Add $x$ to $X$\;
		Add($j$, $L[j][1]$, $Queue$) \tcp*{add the $j$-th list 1st element back}
	}
	\Return $X$\;
\end{algorithm}

\textbf{Complexity}

This algorithm requires $O(n)$ Extract-min and $O(n)$ Add. Each Add 
operation has complexity $O(\log k)$. Thus the total complexity is
$O(n \log k)$


\end{exercise}

\begin{exercise}[Computation of the Fibonacci number]
We shall make use of the following relation
\begin{equation}
	\begin{pmatrix}
		1 & 1\\ 1 & 0
	\end{pmatrix}
	\begin{pmatrix}F(n-1)\\F(n-2)\end{pmatrix}
	= \begin{pmatrix}F(n)\\F(n-1)\end{pmatrix}
\end{equation}
Clearly, from this we obtain
\begin{equation}
	A^n [F(0), F(1)]^T = [F(n), F(n-1)]^T
\end{equation}
where $A = \begin{pmatrix}1 & 1\\ 1 & 0\end{pmatrix}$.

\begin{algorithm}[H]
	\caption{Fib($n$)}
	Let $A$ be the matrix $\begin{pmatrix}1 & 1\\ 1 & 0\end{pmatrix}$\;
	M = exponential-by-squaring($A$, $n$)\;
	$F(n)$ = multiply($M,[1, 1]$)[0]\;
	\Return $F(n)$
\end{algorithm}


\textbf{Complexity}

Computing $A^n$ takes $O(\log n)$ matrix multiplication (of constant
size), thus the time complexity is $O(\log n)$.
\end{exercise}
\begin{exercise}[Computing maximum sum of contiguous subarray]\

\textbf{a)} Denoting $S(i, j)$ as the sum of the array starting
from the $i$-th element to the $j$-th element, that is
\[
	S(i, j) = \begin{cases}
		0 \text{ if $i < j$}\\
		\sum_{k=i}^j L[k] \text{ otherwise}\\
	\end{cases}
\]
\begin{algorithm}[H]
	\caption{Naive summation}
	Let $(1, 1)$ be the selected elements\;
	Let sum = $-\infty$ \;
	Initialize S as a n-by-n zero matrix\;
	\For{$i$ in $[1,...,n]$}{
		\For{$j$ in $[1,...,n]$}{
			\If{j $>$ i}{
			$S[i, j] = S[i, j - 1] + L[j]$\;
			\If{$S[i, j] > sum$}{
			select i, j\;
			sum = S[i, j]
			}
			}
		}
	}
	\Return sum
\end{algorithm}
\textbf{b)} Defining $S_{left}[i]$
as the sum of all element on the left of $j$ including $j$
\[
	S_{left}[i] = \sum_{j=1}^i L[j].
\]

Next, we find two elements $e_{min}$ and $e_{max}$ such that
\[
\begin{aligned}
	e_{min} = \argmin_i S_{left}[i],\\
	e_{max} = \argmax_i S_{left}[i].\\
\end{aligned}
\]
Now, the maximum contiguous sub-array is given by $[e_{min}+1,...,e_{max}]$.

\begin{algorithm}[H]
\label{algo:max-contiguous-array}
\caption{Find maximum contiguous array(L)}
Initialize zero array with length $n$ $S_{left}$\;
Let $S_{left}[1]$ = $L[1]$\;
\For {$i$ in $[2,...n]$}{
	$S_{left}[i] = S_{left}[i-1] + L[i]$
}
Let $e_{min}$ = $e_{max}$ = 1\;
\For {$i$ in $1,...n$}{
	\If{$S_{left}[i] \geq S_{left}[e_max]$}{
	$e_{max} = i$\;
	}
	\If{$S_{left}[i] \leq S_{left}[e_min]$}{
	$e_{min} = i$\;
	}
}
\Return $[e_{min} +1, ..., e_{max}]$
\end{algorithm}

\textbf{Complexity}

Time complexities of all operations are $\Theta(n)$.

\begin{proposition}
Algorithm~(\ref{algo:max-contiguous-array}) returns the maximum contiguous
sub-array.
\end{proposition}

\begin{proof}
To show that our algorithm produces correct result, we start from the
problem statement
\[
	\begin{aligned}
	&\max_{i, j} \sum_{k=i}^j L[k] \\
	=&\max_{i, j} \left( \sum_{k=1}^j L[k] - \sum_{k=1}^{i-1} L[k] \right)\\
	=&\max_{j} \sum_{k=1}^j L[k] - \min_{i}\sum_{k=1}^{i-1} L[k] 
	\end{aligned}
\]
Our algorithm produces the corresponding $\argmax_j\sum_{k=1}^j L[k]$ 
and $\argmin_i\sum_{k=1}^{i-1} L[k]$.
\end{proof}
\end{exercise}

\begin{exercise}[Arbitrage]\

Compute the logarithm of the exchange matrix $R[,]$, then construct
a graph based on this matrix. Find negative cycle on this graph 
using Floyd-Warshall.

\begin{algorithm}[H]
\caption{Arbitrage Opportunity($R[:, :]$)}
\label{algo:negative-arbitrage}
	Let $Adj[:, :] = -\log R[:,:]$ \tcp*{Component-wise logarithm}
	Construct the graph $G(Adj)$\;
	negative-cycle = Floyd-Warshall($G$)\;
	\Return negative-cycle
\end{algorithm}

\begin{proposition}[Correctness]
Algorithm~(\ref{algo:negative-arbitrage}) returns a correct arbitrage
opportunity.
\end{proposition}

\begin{proof}
Let $i_1, i_2, ..., i_k$ be the cycle found by Floyd-Warshall algorithm,
\[
\begin{aligned}
&- \log R[i_1, i_2] - \log R[i_2, i_3] - ... - \log R[i_k, i_1] < 0 \\
\implies&\log (R[i_1, i_2]R[i_2, i_3]...R[i_k, i_1]) > 0\\
\implies&R[i_1, i_2]R[i_2, i_3]...R[i_k, i_1] > 1.
\end{aligned}
\]
\end{proof}
\end{exercise}	
\begin{exercise}
The idea is via max-flow reformulation of the bipartite matching graph. 
More specifically, we add a source node $s$ directly connects to all vertices in $R$ with
edges having capacity of 1. Similarly, a  sink node $t$ connected to all vertices
in $L$ with edges having capacity of 1. Referring to the newly formulated flow
problem as $G$ and the matching as a flow $f$, we first construct the residual 
graph $G_f$. Then, we use DFS to find if there exist a path on $G_f$ that connects
$s$ and $t$. If there is then the matching is not the maximum.
\begin{algorithm}
	\caption{Maximum Matching($R, L, E$)}
	\label{algo:maximum-matching}
	Let $G(R\cup L \cup\{s, t\}, E \cup\{\text{sources and sink edges}\})$ \;
	Let $f=M\cup\{\text{edges from $s$ and $t$}\}$ \;
	Compute residual graph $G_f(G, f)$\;
	maximum-matching = DFS($s, t, G_f$) \tcp*{Find a path between $s$ and $t$}
	\Return maximum-matching
\end{algorithm}
\begin{proposition}[Correctness]
Algorithm~(\ref{algo:maximum-matching}) is correct. More specifically, there
exists an augmenting path $P$ between $s$ and $t$ iff $M$ is not a maximum matching.
\end{proposition}
\begin{proof}
There exist an augmenting path, thus
\[
	\text{val}(f) < \text{max-flow}(G).
\]
Now, note that $\text{val}(f) = \text{card}(M)$ by definition of $f$ 
and that $\text{max-flow}(G)=\text{max-card}(R, L, E)$ (Theorem
during lecture). Therefore
\[
	\iff\text{card}(M) < \text{max-card}(R, L, E),
\]
which means $M$ is not the maximum cardinality matching.
\end{proof}
\end{exercise}
\end{document}






















